---
title: "Untitled"
format:
  html:
    theme: superhero
lang: it
execute: 
  eval: true
  echo: false
  
---
```{r}
library(tidyverse)
library(psych)
library(DataExplorer)
library(performance)
library(ggplot2)
setwd("/Users/riccardopagan/Desktop/MyProject/Data")
```

First I made sure I was in the right directory
```{r comment=""}
setwd("/Users/riccardopagan/Desktop/MyProject/Data")
getwd()
```

Then I merged all my .csv files in a unique dataframe
```{r}
MyData <- read.csv2("308.csv")
len <- nrow(MyData)
IDcol <- rep(308, len)
MyData$ID <- IDcol #adding ID columns 

subjects <- c("309", "310", "330", "331", "332", "333", "334", "335", "337", "349", "350", "351", "352", "369", "370", "371", "372")


for(i in subjects) {
  fname <- paste(i, sep = ".", "csv")
  nfile <- read.csv2(fname)
  len <- nrow(nfile)
  IDcol <- rep(i, len)
  nfile$ID <- IDcol
  MyData <- merge(MyData, nfile, by=c("Reaction", "Days", "ID"), all=TRUE)
}
```

I ordered my new dataframe by ID and Days
```{r}
MyData <- arrange(MyData, ID, Days) 
```

With the merged dataset, I started exploring it.
```{r}
describe(MyData)
plot_intro(MyData)
plot_histogram(MyData$Reaction)
```

After this I started with the true analysis, specifically a linear regression model with days of 
sleep deprivation as predictor. 
```{r}
m1 <- lm (Reaction~Days, data=MyData)
```
And before checking the significance of the model, I visual checked the various assumptions of the model.
```{r}
check_model(m1)
```

Finally I checked the significance of the model
```{r}
summary(m1)
```






:::

:::

# All outputs

::: {.panel-tabset}

## general linear regression

```{r}
ggplot(MyData, aes(x=Days, y=Reaction)) + geom_point() + geom_smooth(method = "lm")
```

## Grafico generale

```{r}
ggplot(MyData, aes(x=Days, y=Reaction)) + geom_point() + geom_smooth(method = "lm")
```

:::
